%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \documentclass{res}
%-----------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\PassOptionsToPackage{hyphens}{url} \usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%-----------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-----------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Ariel Joshua Fogel} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{1949 Hopkins Street} % Your address
\moveleft.5\hoffset\centerline{Berkeley, California 94707}
\moveleft.5\hoffset\centerline{301.325.8434}
\moveleft.5\hoffset\centerline{arielfogel1@gmail.com}

%-----------------------------------------------------------------------------------

\begin{resume}

%-----------------------------------------------------------------------------------
%	EDUCATION
%-----------------------------------------------------------------------------------

\section{\small\bf EDUCATION}
Berkeley City College, Berkeley, CA \hfill Aug. 2017 - Dec. 2017 \\
Dev Bootcamp, San Francisco, CA \hfill June 2014 - Aug. 2014 \\
Muhlenberg College, Allentown, PA \hfill Sept. 2007 - May 2011 \\
{\sl B.A. in Behavioral Economics (Self-Designed) and Music}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Graduated cum laude, with honors in Behavioral Economics
\end{itemize}


%-----------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%-----------------------------------------------------------------------------------

\section{\small\bf EXPERIENCE}

{\sl Research Internship} \hfill May 2018 - Current \\
Computational Approaches to Human Learning @ University of California, Berkeley
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Refactored and augemented functionality of data visualization tool for cluster analysis.
\item Led team focused on testing and continuous integration for the lab's main research project, the AskOski platform.
\item Managed undergraduate researchers, providing debugging assistance, code review, task specifications and prioritization support.
\end{itemize}

{\sl Data Analyst} \hfill July 2018 - Current \\
Masterclass
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Wrote queries, cleaned data, and built Looker dashboards to answer business critical questions for executive team and product managers.
\end{itemize}

{\sl Software Engineer} \hfill Apr. 2015 - Apr. 2017 \\
Bloc Inc.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Team lead on payments-related projects, including proposing and implementing major architectural changes to the automated billing model.
\item Collaborated with stakeholders from multiple teams to prioritize and create feature specifications.
\item Wrote, tested, and deployed backend and frontend features using Ruby on Rails, RSpec, AngularJS 1.3, ES2015 and Mocha.
\end{itemize}

{\sl Software Engineer} \hfill Oct. 2014 - Mar. 2015 \\
Eversight Labs
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Implemented and tested frontend user-flow features using ExtJS framework, Mocha, Chai, and Sinon.
\end{itemize}

{\sl  Research Associate II } \hfill June 2011 - May 2014\\
The Urban Institute
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Wrote Stata programs to run analyses and export data into table and exhibit templates.
\item Coauthored research reports, briefs, and a book chapter.
\item Anonymized and published public use files using survey data from the Massachusetts Health Reform Survey.
\item Gathered, linked, and maintained a central repository of governmental datasets for internal analysis.
\end{itemize}

%-----------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-----------------------------------------------------------------------------------
\section{\small\bf PUBLICATIONS}
McMorrow, S., Long, S. K., \& Fogel, A. (2015). Primary Care Providers Ordered Fewer Preventive Services For Women With Medicaid Than For Women With Private Coverage. {\sl Health Affairs, 34}(6), 1001-1009. doi:10.1377/hlthaff.2014.0907

Long, S. K., Stockley, K., Dahlen, H., \& Fogel, A. (2014). How Will Employers Respond to National Health Reform? Lessons from the 2006 Reform Initiative in Massachusetts. In M. G. Crain \& M. Sherraden (Authors), {\sl Working and Living in the Shadow of Economic Fragility}. New York, NY: Oxford University Press. doi:10.1093/acprof:oso/9780199988488.003.0005

Long, S. K., \& Fogel, A. (2014, March 26). {\sl Health Insurance Coverage and Health Care Access, Use, and Affordability in Massauchusetts: An Update As Of Fall 2012} (Rep.). Retrieved October 10, 2017, from the Blue Cross Blue Shield of Massachusetts Foundation website: \url{https://bluecrossmafoundation.org/sites/default/files/download/publication/MHRS_2012%20Full%20Report.pdf}

Long, S. K., Nordahl, K. W., Walsh, K. K., Hempstead, K., \& Fogel, A. (2014, March 26). Health Insurance Coverage Is Just The First Step: Findings From Massachusetts [Web log post]. Retrieved October 10, 2017, from \url{http://healthaffairs.org/blog/2014/03/26/health-insurance-coverage-is-just-the-first-step-findings-from-massachusetts/}

Holahan, J., Kenney, G. M., Karpman, M., \& Fogel, A. (2014, February 26). {\sl Looking Behind Opinion Polling on the Affordable Care Act} (Rep.). Retrieved October 10, 2017, from The Urban Institute website: \url{http://hrms.urban.org/briefs/aca-opinions.html}

Blavin, F., Hempstead, K., Karpman, M., \& Fogel, A. (2014, February 6). {\sl How the Currently Uninsured Perceive the Cost and Affordability of Health Insurance Coverage} (Rep.). Retrieved October 10, 2017, from The Urban Institue website: \url{http://hrms.urban.org/briefs/uninsured_perceive.html}

Holahan, J., Zuckerman, S., Long, S. K., Goin, D., Karpman, M., \& Fogel, A. (2014, January 28). {\sl Pre-Reform Access and Affordability for the ACA's Subsidy-Eligible Population} (Rep.). Retrieved October 10, 2017, from The Urban Institute website: \url{http://hrms.urban.org/briefs/aca-subsidy-eligible-population.html}

Holahan, J., Zuckerman, S., Long, S. K., Goin, D., Karpman, M., \& Fogel, A. (2014, January 28). {\sl Access and Affordability on the Verge of Health Reform} (Rep.). Retrieved October 10, 2017, from The Urban Institute website: \url{http://hrms.urban.org/briefs/access-and-affordability-on-the-verge.html}


%-----------------------------------------------------------------------------------
%	CONFERENCE PROCEEDINGS SECTION
%-----------------------------------------------------------------------------------

\section{\small\bf CONFERENCE PROCEEDINGS AND \\ PRESENTATIONS}
Fogel, A., \& Dale, D. (2011). {\sl Loss Aversion in Single-Stage Games Mixed Gambles using Real and Hypothetical Incentives.} Presented to the Honors Committee of Muhlenberg College, Allentown, PA.

Kushner, R., \& Fogel, A. (2010, June 30). {\sl Measuring Local Arts Vitality: Lessons from Studies in Cities, Counties, States, and Regions}. Paper presented at the Half-Century Summit Conference of Americans for the Arts, Baltimore, MD.


%-----------------------------------------------------------------------------------

\end{resume}
\end{document}
